%\section{Introduction}
Online video streaming is the most popular service on the Internet. The pervasive penetration of smartphones and the availability of cheap \ac{LTE} networks make it even easier to reach millions of users. Video streaming can be primarily categorized into three categories: i) static video or \ac{VoD} streaming, ii) live video streaming, and iii) interactive video streaming. Video streaming services like YouTube, NetFlix, Amazon Prime videos fall into the video-on-demand category. Here the videos are prerecorded and preprocessed. YouTube-Live, Periscope, Twitch provide services of live video streaming category. From a player's perspective, the only difference between \ac{VoD} and live video streaming is that the videos are not preprocessed in live streaming as it is not ready yet. The services like video conferencing, webinars fall into the third category, the interactive video. The interactive online videos are not only bidirectional but also extremely delay-sensitive. Unlike \ac{VoD} or live streaming, it is okay for interactive video streaming to drop several frames than stall for data. So, the technologies required for interactive videos are very different in every aspect. In our work, we concentrate on the \ac{VoD} and live video streaming over HTTP only.

\ac{HTTP} is a widely accepted protocol as it serves the \ac{WWW}. Most of the firewalls, proxies, and \acr{NAT}-boxes allow \ac{HTTP} protocol. \acsu{HTTPS}, the secure version of \ac{HTTP}, is equally acceptable for the network administrator of different organizations. So, the HTTP(S) based video streaming services also allowed by those firewalls, proxies, and \ac{NAT} boxes. This particular feature increases the popularity of \ac{HTTP(S)}-based video streaming over the existing video streaming systems.

On top of the \ac{HTTP}-based video streaming system, service providers can adapt video quality according to the available network quality using technology like MPEG-DASH, Apple's \ac{HLS}, or Microsoft's SmoothStreaming. These technologies reduce the rebuffering significantly. Currently, most online video services support adaptive video streaming as it provides a better quality of experience to the viewers. Although different organizations develop these technologies, they work almost identically. In our work, we concentrate on \acr{DASH}-based video streaming as it is a guideline than a product, which is widely used in today's video streaming services. Furthermore, the open-source implementation of \ac{DASH} is available for wide-scale implementation and testing.

Depending on the video-streaming environment like the available network bandwidth, \ac{DASH} or \acr{DASH}-like video streaming systems adapt the video quality on-the-fly by running a special algorithm called \ac{ABR} algorithm. The selection of \ac{ABR} is crucial as the overall quality of experience is dependent on the underlying \ac{ABR} algorithm. It is the \ac{ABR} algorithms' job to provide minimal rebuffering while maintaining better video quality. In this chapter, we discuss the basic principles of \ac{DASH} and the details of different components of \ac{DASH}.  We then discuss the latest researches on the \ac{ABR} to improve \ac{QoE} for both {VoD} and live streaming in different scenarios and finally conclude with the available research scopes.

