\section{\textbf{Background and Related Work}}\label{sec:related_work}
% \subsection{Background: DASH system}
%  Adaptive Streaming over HTTP is currently the preferred option for delivering video content.  In \ac{DASH}, a long duration video is broken into chunks of fixed playback time. Successive chunks are aligned in time with each other. Each chunk is stored at \ac{CDN} servers at different bitrates.  A throughput estimator module  estimates the network state, in terms of  the available network throughput, using information on previous chunk downloads. A buffer controller module captures the  video player state using information on streamed video quality and playout-buffer state. Information from both modules are combined by one \ac{ABR} controller to choose an optimal bitrate at which the next chunk is fetched from the \ac{CDN} server. A detailed block diagram of \ac{DASH} can be found in \cite{Sengupta2018} and the references therein.\\
% \indent  State-of-the-art \ac{ABR} algorithms such as MPC \cite{Yin2015}, Pensieve \cite{mao2017neural}, etc. aims to maximize user's \ac{QoE} score, which requires addressing conflicting goals like (a) maximizing overall video quality, (b) minimizing re-buffering time, and (c) increasing smoothness or, i.e., reducing bitrate fluctuations between successive chunks. Due to resource limitations at the client player, complex computations like running a neural network associated with some of these algorithms, e.g. Pensieve,  are run in a stateless \ac{ABR} server. The latency of communication between this server and the \ac{ABR} controller is usually negligible \cite{mao2017neural}. 
%\subsection{RRC state machine of 4G}\label{section:Bckgrd_RRC}
\indent \ac{4G} LTE smartphones are designed to maintain network connectivity using a \ac{RRC} state machine with two states: \textit{CONNECTED} and \textit{IDLE} \cite{Huang2012}. With no active transmission, the \ac{UE} is in the low power \ti{IDLE} state where no radio resource is assigned.  Once a packet arrives, the  \ac{UE} jumps to the high power \ti{CONNECTED} state, in which radio resources are assigned and data transmission takes place.  To reduce the incumbent delay and energy consumption associated with the state promotion, the \ac{UE} waits for a duration called tail time in the \ti{CONNECTED} state before returning to the \ti{IDLE} state even after packet transmission is over. To save energy in the tail period, LTE uses  \ac{DRX} during which the cellular interface periodically monitors the control channel for incoming packets and then goes to sleep ~\cite{Huang2012}. Evidently, if video is downloaded during poor connection quality, then the smartphone will have a longer \ti{CONNECTED} state dwell time resulting in higher energy consumption. Existing \ac{ABR} video streaming algorithms, however, primarily focus on improving \ac{QoE} while paying little attention to energy savings.\\
\noindent \textbf{Improving QoE:}
\ac{ABR} video streaming algorithms either choose buffer occupancy~\cite{Huang2014,Spiteri2016}  or both buffer occupancy and current chunk or network throughput~\cite{Yin2015,Jiang2014,Sengupta2018,Xu2015,Mehr2019} to select optimal bitrates for future video chunks. Examples would be BOLA \cite{Spiteri2016} and MPC \cite{Yin2015}, respectively.
%There are two versions of MPC; Fast MPC- an aggressive approach that uses harmonic mean predictor to estimate future chunk throughput and RobustMPC - a more conservative version which accounts for throughput error. 
Pensieve \cite{mao2017neural} uses a deep RL algorithm for optimal bitrate selection to maximize over a \ac{QoE} metric. However, none of these  works focus on saving device energy consumption under mobility conditions in \ac{4G} LTE networks. \\
\indent In this work, we aim to improve video user's energy consumption over cellular networks while not compromising on \ac{QoE} by tuning playback buffer size to network throughput. Hence, the proposed algorithm should use cellular network throughput prediction.
% \niloy{Does this mean at original level, high definition pictures cannot be seen while here high definition pictures can be seen - this somehow have to come in the study.} \cite{Siris2014} uses mobility and throughput prediction to take decisions on prefetching while moving through a \ac{WiFi}-cellular network.
Several works focus on bandwidth prediction for improving the bitrate selection of  ABR streaming algorithms~\cite{Bentaleb2019,Raca2019,Raca2018_2,yue2018linkforecast}. Some of these works also focus on predicting cellular network throughput~\cite{Raca2019,yue2018linkforecast,Raca2017,Raca2018_2,Raca2018_3,Samba2017, Ghasemi2018}. However, unlike our EnDASH algorithm, none of the works consider the unique situation of co-existence of different technologies and frequent handover from one technology to another for throughput prediction.\\ %In this work, we aim towards using the predicted cellular network throughput to improve energy consumption of \acp{UE}.\\
\noindent\textbf{Reducing Energy Consumption:} Several works in literature investigate energy consumption reduction of mobile phones independently of QoE or ABR streaming algorithms. The BarTendr algorithm in \cite{Schulman2010}  tunes the download sessions in 3G networks to the network conditions for saving energy. However, it quantifies the network condition using received signal strength only while giving no weightage to handovers or associated technologies. GreenTube in \cite{Xin2012} proposes to tune cache management to user behaviour and network conditions. A popular method to reduce energy consumption in mobile phones is to optimize the tail energy, which is achieved in ~\cite{Yang2018} by either prefetching or delaying packets. \\
%\cite{GunerArxiv2018} has proposed power optimization by controlling application-layer parameters such as number of parallel transfers per file, and the number of concurrent fie transfers. \\
%\paragraph{\textbf{\ac{QoS} provisioning for video traffic}} 
% Application layer protocols which prefetch and store video chunks so that the  video quality remains unaffected during poor network conditions are  proposed in \cite{Sengupta2018,Xu2015,Siris2014}. 
\indent To tune packet downloads to network conditions so as to save energy requires a detailed energy profiling of the phones and service providers. This can be obtained through detailed measurement studies as in \cite{Huang2012}. While~\cite{Zhang2018M,Zhang2016,Zhang2016DASH,Khokar2019} focus on the measurement of power consumption of video traffic over HTTP in \ac{4G} networks, the effect of  mobility on signal strength  in \ac{4G} networks is presented briefly. In~\cite{Huang2012, Deng2018} are presented  measurement studies on mobility support in \ac{4G} \ac{LTE} networks. However, to the best of our knowledge, there is no comprehensive measurement study on video streaming under mobility in cellular-only networks. Furthermore, an inherent assumption in these papers is the uninterrupted availability of 4G signal. In contrast, the present work focuses on optimization of energy consumption and \ac{QoE} of mobile video users in scenarios where legacy networks are present in addition to 4G, under mobility conditions.
