\section{\textbf{Conclusion}}\label{section:conclusion}
%In many developing countries, 4G coverage is not ubiquitous. As a result users often have to fallback to legacy networks that support lower throughput, resulting in a higher energy consumption and lower QoE. 
\acresetall
In this report, we propose EnDASH -- an energy aware ABR video streaming algorithm, which minimizes energy consumption while not compromising on QoE of users under mobility. It exploits the high throughput regions in the user's trajectory for aggressive fetching of video chunks thereby reducing energy consumption even in regions with limited 4G coverage and significant presence of legacy networks.  To achieve this, it intelligently tunes the playback buffer length with the average predicted throughput and then resorts to optimal bitrate selection for video chunks. As a result, the buffer length increases sometimes; although, the consequent cost  escalation is negligible. This is because the cost is incurred due to  (a) extra memory usage which is cheap  and can be ignored, and (b) aggressive fetching which may lead to some wastage, but such wastage is rare and minimal, therefore, hardly having any cost impact.\\  %Moreover, the data tariff is extremely cheap ; thus hardly having any impact on the cost.\\
\indent EnDASH predicts the cellular network throughput using Random Forest Learning. It tunes the buffer length and selects the optimal chunk bitrates using Reinforcement learning. EnDASH is able to improve the maximum energy consumption by about 30.4\% in comparison to the popular Pensieve algorithm although with reduction in QoE. Since EnDASH is a tunable algorithm it can be designed to adapt to a specific  requirement, such as energy or QoE -- this would be our immediate future work.  Additionally, our future work will also involve real-life implementation of EnDASH and investigating the corresponding improvement in energy efficiency.

\section*{Publications}

\subsection*{Submitted}
\begin{enumerate}[start=1,label={[\arabic*]}]
	\item \textbf{Abhijit Mondal}, Sandip Chakraborty, ``\textit{An End-to-end protocol over Heterogeneous Internet}'', submitted to Elsevier Computer Networks.
\end{enumerate}

\subsection*{Published:}
\begin{enumerate}[start=1,label={[\arabic*]}]
	\item Nishant Somy, \textbf{Abhijit Mondal}, Bishakh Ghosh, Sandip Chakraborty, ``\textit{System Call Interception for Serverless Isolation}'', in Proceedings of the annual conference of the ACM Special Interest Group on Data Communication (SIGCOMM) 2020 Demos and Posters, New York, USA, August 11 - 14, 2020.
	\item \textbf{Abhijit Mondal}, Sandip Chakraborty, ``\textit{Federated Adaptive Bitrate Live Streaming over Locality Sensitive Playback Coalitions}”, in the Proceedings of the Workshop on Network Application Integration/CoDesign (NAI '20), Association for Computing Machinery, New York, USA, August 11 - 14, 2020. 
	\item \textbf{Abhijit Mondal}, Sandip Chakraborty, ``\textit{Does QUIC Suit Well with Modern Adaptive Bitrate Streaming Techniques?}”, in IEEE Networking Letters, vol. 2, no. 2, pp. 85-89, June 2020.
	\item \textbf{Abhijit Mondal}, Basabdatta Palit, Somesh Khandelia, Nibir Pal, Jay Jayatheerthan, Krishna Paul, Niloy Ganguly and Sandip Chakraborty, ``\textit{EnDASH - A Mobility Adapted Energy Efficient ABR Video Streaming for Cellular Networks}'', in the Proceedings of 2020 IFIP Networking Conference (IFIP Networking), Paris, France, June 22-25, 2020.
	\item Vinnakota Venu Balaji, Naganithin Manne, \textbf{Abhijit Mondal}, Debarati Sen and Sandip Chakraborty, ``\textit{An Experimental Study of C-RAN Fronthaul Workload Characteristics: Protocol Choice and Impact on Network Performance}", in Proceedings of the 89th Vehicular Technology Conference (VTC2019-Spring), Kuala Lumpur, Malaysia, April 28 - May 1, 2019.
	\item \textbf{Abhijit Mondal}, Sourav Bhattacharjee, Sandip Chakraborty, ``\textit{Viscous: An End to End Protocol for Ubiquitous Communication Over Internet of Everything}'' in Proceedings of 42nd Annual IEEE Conference on Local Computer Networks (IEEE LCN 2017), Singapore, October 9-12, 2017.
	\item \textbf{Abhijit Mondal}, Satadal Sengupta, B.R. Reddy, M.J.V. Koundinya, Chander G., Pradipta De, Niloy Ganguly, Sandip Chakraborty, ``\textit{Candid with YouTube: Adaptive Streaming Behavior and Implications on Data Consumption}'' in Proceedings of the 27th Workshop on Network and Operating Systems Support for Digital Audio and Video (ACM NOSSDAV’17), Taipei, Taiwan, June 20 - 23, 2017.
\end{enumerate}