\section{Summary}\label{sec:chap04:conclusion}
%In many developing countries, 4G coverage is not ubiquitous. As a result users often have to fallback to legacy networks that support lower throughput, resulting in a higher energy consumption and lower QoE. 
\acresetall
In this chapter, we propose EnDASH -- an energy aware ABR video streaming algorithm, which minimizes energy consumption while not compromising on QoE of users under mobility. It exploits the high throughput regions in the user's trajectory for aggressive fetching of video chunks thereby reducing energy consumption even in regions with limited 4G coverage and significant presence of legacy networks.  To achieve this, it intelligently tunes the playback buffer length with the average predicted throughput and then resorts to optimal bitrate selection for video chunks. As a result, the buffer length increases sometimes; although, the consequent cost  escalation is negligible. This is because the cost is incurred due to  (a) extra memory usage which is cheap  and can be ignored, and (b) aggressive fetching which may lead to some wastage, but such wastage is rare and minimal, therefore, hardly having any cost impact. %Moreover, the data tariff is extremely cheap ; thus hardly having any impact on the cost.\\
EnDASH predicts the cellular network throughput using Random Forest Learning. It tunes the buffer length and selects the optimal chunk bitrates using Reinforcement learning. EnDASH is able to improve the maximum energy consumption by about 30.4\% in comparison to the popular Pensieve algorithm although with reduction in QoE. 

In this chapter, we have primarily looked into optimizing ABR streaming over buffered videos with an objective of energy saving for the device that runs the video streaming client. As we discussed earlier, another class of video streaming, namely the live streaming, also dominates the current OTT streaming services. In the next chapter, we discuss the development of a live streaming mechanism that saves the bottleneck bandwidth over the Internet, while improving the QoE for the end users by supporting ABR streaming. 