\section{Conclusion}
%The QUIC is a new protocol developed the Google to {\it make web faster}. The Google claims that it performs better than traditional TCP based HTTP/HTTPS connection. Several existing work shows that QUIC performance is comparable to TCP. In this work we have compared QUIC's permance for web based video streaming. Our result shows that QUIC's performance is slightly poorer than the existing TCP in terms of quality of experience.
This work gives an analysis of the recent advanced ABR techniques over the QUIC as the end-to-end transport protocol. We observed that all the ABR techniques are sensitive to sudden increase or drop in the client-perceived link bandwidth, and therefore are more compatible with TCP rather than QUIC. \blue{The QUIC multiplexing of audio and video streams over a single UDP socket results in additional response latency for the audio segments, which are not captured during the calculation of channel throughput. As a consequence, the ABR algorithms take incorrect decisions during selecting the bitrates based on the calculated throughput over a QUIC connection.} The analysis discussed in this work opens up a new direction of research on exploring ABR techniques over QUIC which is the de-factor transport protocol for Google services. 
\\
\\
\section*{Publications}

\subsection*{Submitted}
\begin{enumerate}[start=1,label={[\arabic*]}]
	\item \textbf{Abhijit Mondal}, Sandip Chakraborty, ``\textit{Does QUIC Suit Well with Modern Adaptive Bitrate Streaming Techniques?}'', major revision submitted to the IEEE Networking Letters.
	\item \textbf{Abhijit Mondal}, Sandip Chakraborty, ``\textit{Federated Live Streaming with DASH Support}'', submitted to the 28th International Conference on Computer Communication and Networks (ICCCN), Honolulu, Hawaii, USA, August 3 - 6, 2020.
	\item \textbf{Abhijit Mondal}, Sandip Chakraborty, ``\textit{An End-to-end protocol over Heterogeneous Internet}'', submitted to Elsevier Computer Networks.
\end{enumerate}

\subsection*{Published:}
\begin{enumerate}[start=1,label={[\arabic*]}]
	\item \textbf{Abhijit Mondal}, Basabdatta Palit, Somesh Khandelia, Nibir Pal, Jay Jayatheerthan, Krishna Paul, Niloy Ganguly and Sandip Chakraborty, ``\textit{EnDASH - A Mobility Adapted Energy Efficient ABR Video Streaming for Cellular Networks}'', accepted in Proceedings of 2020 IFIP Networking Conference (IFIP Networking), Paris, France, June 22-25, 2020.
	\item \textbf{Abhijit Mondal}, Sourav Bhattacharjee, Sandip Chakraborty, ``\textit{Viscous: An End to End Protocol for Ubiquitous Communication Over Internet of Everything}'' in Proceedings of 42nd Annual IEEE Conference on Local Computer Networks (IEEE LCN 2017), Singapore, October 9-12, 2017.
	\item \textbf{Abhijit Mondal}, Satadal Sengupta, B.R. Reddy, M.J.V. Koundinya, Chander G., Pradipta De, Niloy Ganguly, Sandip Chakraborty, ``\textit{Candid with YouTube: Adaptive Streaming Behavior and Implications on Data Consumption}'' in Proceedings of the 27th Workshop on Network and Operating Systems Support for Digital Audio and Video (ACM NOSSDAV’17), Taipei, Taiwan, June 20 - 23, 2017.
\end{enumerate}