\section{Conclusion}
In this work, we develop a system for edge-assisted collaborative adaptive live streaming which improves the overall QoE and the average video quality for every player. The architecture utilizes a federated platform where the streaming players form coalitions and schedule video downloads among the coalition members in a decentralized way. The proposed architecture has been implemented and evaluated over a thorough emulation platform, and we observe significant improves in overall QoE with reduction in the load at the live streaming server. In the future, we plan to explore reinforcement learning strategies to make the schedule more robust with less gossiping overhead among coalition members. 

\section*{Publications}

\begin{enumerate}[label=\arabic*.]
	\item \textbf{Abhijit Mondal}, Sandip Chakraborty, ``\textit{Federated Live Streaming with DASH Support'}'', submitted to IEEE Global Communications Conference (GLOBECOM 2019) 9-13 December 2019, Waikoloa, HI, USA.
	\item \textbf{Abhijit Mondal}, Sandip Chakraborty, ``\textit{An End-to-end protocol over Heterogeneous Internet}'', submitted to IEEE Transactions on Network and Service Management.
	\item \textbf{Abhijit Mondal}, Sourav Bhattacharjee, Sandip Chakraborty, ``\textit{Viscous: An End to End Protocol for Ubiquitous Communication Over Internet of Everything}'' in Proceedings of 42nd Annual IEEE Conference on Local Computer Networks (IEEE LCN 2017), Singapore, October 9-12, 2017.
	\item \textbf{Abhijit Mondal}, Satadal Sengupta, B.R. Reddy, M.J.V. Koundinya, Chander G., Pradipta De, Niloy Ganguly, Sandip Chakraborty, ``\textit{Candid with YouTube: Adaptive Streaming Behavior and Implications on Data Consumption}'' in Proceedings of the 27th Workshop on Network and Operating Systems Support for Digital Audio and Video (ACM NOSSDAV'17), Taipei, Taiwan, June 20 - 23, 2017.
\end{enumerate}

%\noindent\hspace{5mm}[1] Abhijit Mondal, Sandip Chakraborty, ``\textit{Federated Live Streaming with DASH Support'}'', submitted to IEEE Global Communications Conference (GLOBECOM 2019) 9-13 December 2018, Waikoloa, HI, USA.
%
%\noindent\hspace{5mm}[2] Abhijit Mondal, Sandip Chakraborty, ``\textit{An End-to-end protocol over Heterogeneous Internet}'', submitted to IEEE Transactions on Network and Service Management.
%
%\noindent\hspace{5mm}[3] Abhijit Mondal, Sourav Bhattacharjee, Sandip Chakraborty, ``\textit{Viscous: An End to End Protocol for Ubiquitous Communication Over Internet of Everything}'' in Proceedings of 42nd Annual IEEE Conference on Local Computer Networks (IEEE LCN 2017), Singapore, October 9-12, 2017.
%
%\noindent\hspace{5mm}[4] Abhijit Mondal, Satadal Sengupta, B.R. Reddy, M.J.V. Koundinya, Chander G., Pradipta De, Niloy Ganguly, Sandip Chakraborty, ``\textit{Candid with YouTube: Adaptive Streaming Behavior and Implications on Data Consumption}'' in Proceedings of the 27th Workshop on Network and Operating Systems Support for Digital Audio and Video (ACM NOSSDAV'17), Taipei, Taiwan, June 20 - 23, 2017.
