
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\Acknowledgments{

\addcontentsline{toc}{chapter}{Acknowledgements}
\fontsize{12}{13}\selectfont %\dropping[0cm]{2}
Many people supported me during the journey, and it is my honor to acknowledge them. At first, I like to express my gratitude towards my supervisor Prof. Sandip Chakraborty for his immense help, motivation, guidance to carry out this work. His continuous support in the form of discussions, constructive criticisms, and clear understandings has helped me proceed in the right direction. I am really indebted to him for giving me a wide exposure to the field of computer networks and online video streaming and helping me to contribute constructively to this field. In this entire tenure, he was not only my supervisor but also a friend whom I could always count. It was impossible to complete this work without his support.

I will forever be thankful to Dr. Niloy Ganguly for encouraging me to take up this Ph.D. journey and the support he provided both on the research and career front. I would extend Prof. Animesh Mukherjee, Prof. Bivas Mitra, and Prof. Gautam Das to serve on my doctoral scrutiny committee and for their valuable advice and suggestions. I am privileged to thank Prof. Arobinda Gupta, Prof. Payan Goyel, Prof. Palash Dey for the lessons and experience during several classes and TA sessions. It is an honor to get in touch with Rajeev Shorey, and I thank him for introducing me to the extensive network of researchers. I would like to thank Bappa da, Hoimanti di, Ashokbabu, Swapanbabu, Prasunda, and all other office members for being helpful in sorting out all the official work.

It is my pleasure to thank Ayan da, Subhrangsu da, Soumadip, Snigdha, Soumyajit, Bishakh, Basabdatta di (BD) for the company and support throughout the period and the encouragement to finish the thesis. I am also grateful to Surjya da, Ayan, Bidisha, Satadal, Rohit, Madhumita, Soumajit (halum), Abir da for the inspiration they provided. The campus life would not be memorable without Bijoy, Anupam, Sueet, Alapan, Ashutosh, Suravi. I thank every member of CNeRG for being there whenever I needed some help. My acknowledgment would not complete without saying thanks to Pala for the various insight before and during the period.

My greatest strength comes from my family. My parents and my sister have been my greatest source of inspiration. Without their patience, constant encouragement, support, unparalleled love, prayers, and well wishes, I could never have completed this endeavor. I am what I am because of them. My sister, Dipa, was always there for me and always ready to bring a smile to me.

% {\chancery 
%This thesis would not have seen the light of day without the help and support of many people. I would like to express my gratitude towards my supervisor Prof. Sudeshna Sarkar for her immense help, motivation, and guidance to carry out this work. Her continued support in the form of discussion, constructive criticism, and clear understanding has helped me to proceed in the right direction. I am really indebted to her for giving me a wide exposure to the field of natural language processing and helping me to contribute constructively to this field. Without her invaluable advice and supervision, it would not be possible to complete this work. I am grateful to Prof. Pabitra Mitra, Prof. Jayanta Mukhopadhyay, Prof. Pawan Goyal, and Prof. Shamik Sural for serving on my doctoral scrutiny committee and for their valuable advise and suggestions. Finally, I would like to thank Prof. Sudebkumar Prasant Pal, Prof. Debdeep Mukhopadhyay, Prof. Dipanwita Roy Chowdhury, Prof. Pallab Dasgupta and Prof. Niloy Ganguly for teaching me different subjects that helped me in carrying out my research. I would like to thank Bappada, Ashokda, Swapanbabu, Shibuda, Prasunda, Prasenjitda, Durgada and all other office members for being helpful in sorting out all the official work.
%
%% CHANGE THIS PARA
%I feel blessed to have friends like Rajorshee (Jalu), Subhrangshu (\textit{SM}), Abhijit, Ashutosh, Soumadip, Bijoy, A(-CM)bhik, Rajibda and Arnab. Without their company and support, it would have been difficult to complete my PhD. I would like to acknowledge my gratitude towards my seniors Joyda, Kunalda, Aritrada, Sumantada, Sudakshinadi, Antaradi, Priyankadi and Subhasishda for their unconditional support and valuable advice. I thank Tapas, Bidisha, Kalyani, Anirban, Paheli, Parthada, Devleena, Alapan, Arpita, Anupam, Subhajit, Debasish, Sibendu, Pawan, Aliba, Avik and Anupamda for making my stay at IIT Kharagpur a memorable one.
%
%I would like to take this opportunity to thank Dr. Mandar Mitra and Mr. Niharendu Mukhopadhyay who have always inspired me with their unconditional support and encouragement throughout this journey.
%
%My greatest strength comes from my family. My parents have been my greatest source of inspiration. Without their patience, constant encouragement, support, unparalleled love, prayers and well wishes, I could never have completed this endeavour. I am what I am because of them. I would also like to express my gratitude towards my aunts, brothers and sisters-in-law for their constant support and encouragement. I am grateful towards my niece and nephew for being  constant sources of smile for me.\\\\
\begin{flushright}
\medskip

\studname\\

\end{flushright}

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

