\Bio{
Abhijit Mondal has completed his Bachelor of Technology (B. Tech) degree from the Maulana Abul Kalam Azad University of Technology (MAKAUT), West Bengal (former West Bengal University of Technology) in 2010 and Master in Technology (M. Tech) from the Indian Institute of Technology Guwahati in 2012. He has an industry experience at Rovi (now Tivo) as a Software Developer for 2.5 Years (2012 - 2015). He joined for Ph.D. at the Indian Institute of Technology, Kharagpur in 2015. His research interests are in computer networks, specifically in network protocol design and network application development.

\begin{center}
	\Large{{\bf All Publications by the Author}}
\end{center}

\begin{enumerate}
\item Nishant Somy, \textbf{Abhijit Mondal}, Bishakh Ghosh, and Sandip Chakraborty, ``\textit{System Call Interception for Serverless Isolation}", in Proceedings of the Annual Conference of the ACM Special Interest Group on Data Communication on the Applications, Technologies, Architectures, and Protocols for Computer Communication (ACM SIGCOMM '20) -- Demos and Posters, August 10 - 14, 2020.
\item \textbf{Abhijit Mondal}, and Sandip Chakraborty, ``\textit{Does QUIC Suit Well with Modern Adaptive Bitrate Streaming Techniques?}”, in IEEE Networking Letters, vol. 2, no. 2, pp. 85-89, June 2020.
\item \textbf{Abhijit Mondal}, and Sandip Chakraborty, ``\textit{Federated Adaptive Bitrate Live Streaming over Locality Sensitive Playback Coalitions}”, in Proceedings of the ACM SIGCOMM Workshop on Network Application Integration/CoDesign (ACM SIGCOMM NAI '20), Online, August 11 - 14, 2020. 
\item \textbf{Abhijit Mondal}, Basabdatta Palit, Somesh Khandelia, Nibir Pal, Jay Jayatheerthan, Krishna Paul, Niloy Ganguly, and Sandip Chakraborty, ``\textit{EnDASH - A Mobility Adapted Energy Efficient ABR Video Streaming for Cellular Networks}'', in Proceedings of the 2020 IFIP Networking Conference (IFIP Networking), Online, June 22-25, 2020.
\item Venu Balaji Vinnakota, Naganithin Manne, \textbf{Abhijit Mondal}, Debarati Sen, and Sandip Chakraborty ``\textit{An Experimental Study of C-RAN Fronthaul Workload Characteristics: Protocol Choice and Impact on Network Performance}'', in Proceedings of the IEEE 89th Vehicular Technology Conference (VTC2019-Spring), Kuala Lumpur, Malaysia, 2019.
\item \textbf{Abhijit Mondal}, Sourav Bhattacharjee, and Sandip Chakraborty, ``\textit{Viscous: An End to End Protocol for Ubiquitous Communication Over Internet of Everything}" in Proceedings of the IEEE 42nd Conference on Local Computer Networks (LCN), Singapore, 2017.
\item \textbf{Abhijit Mondal}, Satadal Sengupta, B.R. Reddy, M.J.V. Koundinya, Chander G., Pradipta De, Niloy Ganguly, Sandip Chakraborty, ``\textit{Candid with YouTube: Adaptive Streaming Behavior and Implications on Data Consumption}'' in Proceedings of the 27th ACM Workshop on Network and Operating Systems Support for Digital Audio and Video (ACM NOSSDAV’17), Taipei, Taiwan, June 20 - 23, 2017.

\end{enumerate}
}