\chapter*{Disseminations from the Thesis}
\vspace*{0.5cm}
% \noindent
\renewcommand{\chaptermark}[1]{\markboth{}{\sffamily #1}}
\chaptermark{Dissemination}

\section*{Journal}
\begin{enumerate}[start=1,label={[\arabic*]}]
	\item \textbf{Abhijit Mondal}, and Sandip Chakraborty, ``\textit{Does QUIC Suit Well with Modern Adaptive Bitrate Streaming Techniques?}”, in IEEE Networking Letters, vol. 2, no. 2, pp. 85-89, June 2020.
\end{enumerate}

\section*{Conference and Workshop Proceedings}
\begin{enumerate}[start=1,label={[\arabic*]}]
	\item \textbf{Abhijit Mondal}, and Sandip Chakraborty, ``\textit{Federated Adaptive Bitrate Live Streaming over Locality Sensitive Playback Coalitions}”, in the Proceedings of the ACM SIGCOMM Workshop on Network Application Integration/CoDesign (ACM SIGCOMM NAI '20), Online, August 11 - 14, 2020. 
	\item \textbf{Abhijit Mondal}, Basabdatta Palit, Somesh Khandelia, Nibir Pal, Jay Jayatheerthan, Krishna Paul, Niloy Ganguly and Sandip Chakraborty, ``\textit{EnDASH - A Mobility Adapted Energy Efficient ABR Video Streaming for Cellular Networks}'', in the Proceedings of 2020 IFIP Networking Conference (IFIP Networking), Online, June 22-25, 2020.
	\item \textbf{Abhijit Mondal}, Satadal Sengupta, B.R. Reddy, M.J.V. Koundinya, Chander G., Pradipta De, Niloy Ganguly, Sandip Chakraborty, ``\textit{Candid with YouTube: Adaptive Streaming Behavior and Implications on Data Consumption}'' in Proceedings of the 27th ACM Workshop on Network and Operating Systems Support for Digital Audio and Video (ACM NOSSDAV’17), Taipei, Taiwan, June 20 - 23, 2017.
\end{enumerate}
%\begin{center}
%\textbf{\underline{Journals}}
%\end{center}
%\begin{enumerate}
%\item journal 1
%\end{enumerate}
%
%\begin{center}
%{\textbf{\underline{Conferences}}}
%\end{center}
%% \subsection*{Conferences}
%
%\begin{enumerate}
%\item conf 1
%
%\end{enumerate}
%% \endgroup
%\noindent
%% \rule{0.49\textwidth}{0.75pt} $_{\Diamond}$ \rule{0.49\textwidth}{0.75pt}\\
%
%% \end{onehalfspacing}




